Behavior Driven Development in Haskell

### 2012-06-02 paper.tex
Implementation: Haddock: wording
Implementation: Doctest: wording

To extract evidence from Haddock comments,
Doctest used the Haddock API in the past.
Since each release of Haddock supports only the latest version of GHC,
it is difficult to support old versions of GHC with Haddock API.
Doctest is now directly using GHC API for portability.

>>>>

To extract evidence from Haddock comments,
Doctest initially used the Haddock API.
Since each release of Haddock only supports the latest version of GHC,
it was difficult to support old versions of GHC with Doctest.
Doctest now uses the GHC API directly for portability.
